Supervision

### 2024-12-12 supervision.qmd
update

-   Vesko Varbanov (2020-) ' Sensory processing in Autism Spectrum Conditions and Attention Deficit Hyperactivity Disorder'

>>>>

-   James Myers (2022-) 'Modelling cognitive decline in dementia patients: the impact of social isolation'

-   Vesko Varbanov (2020-) 'Sensory processing in Autism Spectrum Conditions and Attention Deficit Hyperactivity Disorder'
